Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2020-03-06 slides/ExpSlides.tex
1. first round of results with SMM. mostly work. need to clean up the difference between -dev and orginal files.

\section{Estimation}
\begin{frame}{Minimum distance estimation}

@@

	\begin{itemize}
		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni} \} \times \{ar, sv\}$
		\item  $\Gamma$: constraints for the parameter. 
		\item $M_{data}$: data moments
		\item $F$ model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up to each point of the time $t$
		\item  $W$: weight matrix, identity matrix for now 
	\end{itemize}

@@

\begin{frame}{Results: professionals and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SPF}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Results: households and SEAR}
	\begin{figure}[ht]
	\label{SE_diag_SCE}
	\begin{subfigure}[b]{0.19\textwidth}
		\centering
		\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.19\textwidth}
		\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
	\end{subfigure}
\hfill
\begin{subfigure}[b]{0.19\textwidth}
	\caption{forecast/FE}
	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.19\textwidth}
	\caption{FE/var}
	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.19\textwidth}
	\caption{FE/var/Disg}
	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag4.png}
\end{subfigure}
\end{figure}
\end{frame}

\begin{frame}{SE parameter estimate}
	\begin{table}
		\centering
		\caption{Minimum Distance Estimates of Parameters of SE}
		\label{GMM_Est_SE_Table}
		\begin{tabular}{lllll}
			\hline 
			0        & 1    & 2   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
			\hline 
			Forecast &      &     & 0.04                       & 1                          \\
			FE       &      &     & 0.05                       & 0.19                       \\
			FE       & Disg &     & 0.17                       & 0.19                       \\
			FE       & Var  &     & 0.16                       & 0.18                       \\
			FE       & Disg & Var & 0.53                       & 0.18                      \\
			\hline 
		\end{tabular}
	\end{table}
\begin{itemize}
	\item $\lambda$: update rate in SE
\end{itemize}
\end{frame}

\begin{frame}{Results: professionals and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SPF}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Results: households and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SCE}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{NIAR parameters}
	\begin{table}
		\centering
		\caption{Minimum Distance Estimates of Parameters of NI}
		\label{GMM_Est_NI_Table}
		\begin{tabular}{llllll}
	\begin{tabular}{lllllll}
		\hline 
		0        & 1    & 2   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
		\hline 
		Forecast &      &     & 39.65                     & 192.22                & 2.35                      & 0.38                  \\
		FE       &      &     & 12.64                     & 211.14                & 1.64                      & 0                     \\
		FE       & Disg &     & 112.37                    & 0.34                  & 512.51                    & 0.86                  \\
		FE       & Var  &     & 1.13                      & 367.43                & 0                         & 1.28                  \\
		FE       & Disg & Var & 1.29                      & 29.84                 & 2.74                      & 127.86                \\
		\hline 
	\end{tabular}  
		\end{tabular}
	\end{table}	
\begin{itemize}
	\item $\sigma_{pb}$: noisiness of public signals in NI
	\item $\sigma_{pr}$: noisiness of private signals in Ni 
\end{itemize}
\end{frame}

@@

\begin{frame}{Results: professionals and SESV}
	\begin{figure}[ht]
		\label{SESV_diag_SPF}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

>>>>

\section{Estimation}
\begin{frame}{Simulated method of moment estimation}

@@

	\begin{itemize}
		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni} \} \times \{ar, sv\}$
		\item  $\Gamma$: constraints for the parameter. 
		\item $M_{data}$: data moments
		\item $F$: simulated model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up till each point of the time $t$. 
		\begin{itemize}
			\item unconditional moments, not specific to time
			\item moments selected from average forecast, variance and autocovariance of forecasts, average diagreement, variance and autovariance of disagreement, average uncertainty, etc. 
		\end{itemize}
		\item  $W$: weight matrix, identity matrix for now 
	\end{itemize}
\end{frame}

\begin{frame}{Estimation procedure and algorithm}
	\begin{enumerate}
		\item for each theory of expectation formation and the inflation process, start with an initial value for the parameter(s) of interest
		\item simulate individual forecasts for a large enough ($N=200$) number of forecasters
		\item compute the average forecast errors, disagreement and average uncertainty across all agents
		\item compute the time-series moments of the average forecast, disagreement, and uncertainty
		\item compute the difference between the simulated moments and the data moments 
		\item keep searching the parameter value until reaching below a threshold of the loss
	\end{enumerate}
\end{frame}

\begin{frame}{Two-step and joint estimation}
	\begin{enumerate}
		\item two-step estimation:  separately estimate inflation process parameters and then parameters of the inflation process
		\begin{itemize}
			\item pros: computationally lighter 
			\item cons: potential misspecification. does not utilize the expectation data to understand inflation process per se.  
		\end{itemize}
		\item joint estimation: targeting both moments of realized inflation series and moments of forecasts to simultaneously estimate both the inflation process and the parameter of expectation formation
		\begin{itemize}
			\item pros: additional information gain from expectations data about inflation process itself
			\item cons: more computation burden  
		\end{itemize}
	\end{enumerate}
\end{frame}

@@

\begin{frame}{Professionals and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{Professionals and SEAR: joint estimation}
	\begin{figure}[ht]
		\label{SE_diag_SPF_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_joint_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{Households and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{Households and SEAR: joint estimates}
	\begin{figure}[ht]
		\label{SE_diag_SCE_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
		\end{subfigure}
		\hfill
	\end{figure}
\end{frame}

\begin{frame}{SE parameter estimate}
	\begin{table}
		\centering
		\caption{SMM Estimates of Parameters of SE}
		\label{SMM_Est_SE_Table}
	\begin{tabular}{llllllllllll}
		\hline 
		0     & 1       & 2       & 3       & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
		\hline 
		FEVar & FEATV   &         &         & 0.47                       & 0.36                       & 1          & 0.08         & 0.2                        & 0.59                       & 0.99       & 0.08         \\
		FEVar & DisgATV & DisgVar &         & 0.27                       & 0.38                       & 1          & 0.11         & 0.2                        & 0.56                       & 0.98       & 0.08         \\
		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08         \\
		FEVar & FEATV   & DisgVar & DisgATV & 0.47                       & 0.36                       & 1          & 0.1          & 0.2                        & 0.59                       & 0.99       & 0.08        \\
		\hline 
	\end{tabular}
	\end{table}
\begin{itemize}
	\item $\lambda$: update rate in SE
\end{itemize}
\end{frame}

\begin{frame}{Professionals and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
		\end{subfigure}
	\end{figure}
	\end{frame}

\begin{frame}{Professionals and NIAR: joint estimates}
	\begin{figure}[ht]
		\label{NI_diag_SPF_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_joint_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SCE}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Households and NIAR: joint estimates}
	\begin{figure}[ht]
		\label{NI_diag_SCE_joint}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_joint_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

@@

\begin{frame}{Professionals and SESV}
	\begin{figure}[ht]
		\label{SESV_diag_SPF}
		\begin{subfigure}[b]{0.2\textwidth}
			\centering
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.2\textwidth}
			\caption{FE/Disg/Var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{NIAR parameters}
	\begin{table}
		\centering
		\caption{SMM Estimates of Parameters of NI}
		\label{SMM_Est_NI_Table}
		\begin{tabular}{llllll}
		\begin{tabular}{lllllllllllllllll}
			\hline 
			0       & 1       & 2       & 3       & 4   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
				\hline 
			FEVar   & FEATV   &         &         &     & 25.32                     & 16.07                 & 0.9                       & 1.09                  & 1          & 0            & 3.4                       & 15.4                  & 3.4                       & 11.29                 & 1          & 0            \\
			DisgVar & DisgATV &         &         &     & 471301.73                 & 0.85                  & -1.74                     & -0.17                 & 0.91       & 0.42         & 168519.46                 & 1.09                  & 0.67                      & 0.58                  & 1          & 0.03         \\
			FEVar   & FEATV   & DisgVar & DisgATV &     & 25.32                     & 16.07                 & 0.9                       & 1.09                  & 1          & 0            & 3.4                       & 15.4                  & 3.4                       & 11.29                 & 1          & 0            \\
			FEVar   & FEATV   & DisgVar & DisgATV & Var & 9.16708E+12               & 2.37                  & 0.9                       & 1.09                  & 1          & 0            & 13.22                     & 59.96                 & 13.22                     & 59.96                 & 1          & -0.03       \\
			\hline 
		\end{tabular}
		\end{tabular}
	\end{table}	
	\begin{itemize}
		\item $\sigma_{pb}$: noisiness of public signals in NI
		\item $\sigma_{pr}$: noisiness of private signals in Ni 
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Stocastic volatility (old)}
